### 2020-09-17 priority-gv.tex
Finished OC-Completeness.
Extended congruence, finished proof of SC correspondence.
Updated translation to configurations so OC is complete.
Restore absurd, many other changes. I should be better at atomic commits.

\subsubsection{Syntactic Sugar}%
\label{sec:pgv-syntax-sugar}
We define the type of pure functions, \ie functions which perform no communication:
\[
  \ty{\tylolli{T}{U}} \elabarrow \ty{\tylolli[\cs{\ptop},\cs{\pbot}]{T}{U}}
\]
We define sequential composition, let-binding, and various pattern matching lambda abstractions:
\[
\begin{array}{lcl}
  \tm{\andthen{M}{N}}
  & \elabarrow & \tm{\letunit{M}{N}} \\
  \tm{\letbind{x}{M}{N}}
  & \elabarrow & \tm{(\lambda x.N)\;M} \\
  \tm{\lambda\unit.M}
  & \elabarrow & \tm{\lambda z.\letunit{z}{M}} \\
  \tm{\lambda\pair{x}{y}.M}
  & \elabarrow & \tm{\lambda z.\letpair{x}{y}{z}{M}}
\end{array}
\]
We define fork, which combines channel creation and thread spawning in one construct:
\[
\begin{array}{lcl}
  \tm{\fork}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\spawn\;{(\lambda\unit.x\;y)}}{z}}}
\end{array}
\]
We define types for internal and external choice, and their corresponding communication constructs:
\[
\begin{array}{lcl}
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}}
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
\end{array}
\]
\[
\begin{array}{lcl}
  \tm{\select{\ell}}
  & \elabarrow & \tm{\lambda x.\fork\;{(\lambda y.\send\;{\pair{\ell\;y}{x}})}} \\
  \tm{\offer{L}{x}{M}{y}{N}}
  & \elabarrow & \tm{\letpair{z}{w}{\recv\;{L}}{\wait\;{w};}} \\
  &            & \quad\tm{\casesum{z}{x}{M}{y}{N}} \\
  \tm{\offeremp{L}}
  & \elabarrow & \tm{\letpair{z}{w}{\recv\;L}{\andthen{\wait\;{w}}{\absurd{z}}}}
\end{array}
\]

@@

\subsubsection{Structural congruence}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{SC-LinkSwap}   & \tm{\plug{\conf{F}}{\link\;{\pair{x}{y}}}}
                               & \equiv & \tm{\plug{\conf{F}}{\link\;{\pair{y}{x}}}}
    \\
    \LabTirName{SC-ResSwap}    & \tm{\res{x}{y}{\conf{C}}}
                               & \equiv & \tm{\res{y}{x}{\conf{C}}}
    \\
    \LabTirName{SC-ResComm}    & \tm{\res{x}{y}{\res{z}{w}{\conf{C}}}}
                               & \equiv & \tm{\res{z}{w}{\res{x}{y}{\conf{C}}}}
    \\
    \LabTirName{SC-ResExt}     & \tm{\res{x}{y}{(\ppar{\conf{C}}{\conf{D}}})}
                               & \equiv & \tm{\ppar{\conf{C}}{\res{x}{y}{\conf{D}}}},
                                          \text{ if }{\tm{x},\tm{y}\notin\fv(\tm{\conf{C}})}
    \\
    \LabTirName{SC-ParNil}     & \tm{\ppar{\conf{C}}{\child{\unit}}}
                               & \equiv & \tm{\conf{C}}
    \\
    \LabTirName{SC-ParComm}    & \tm{\ppar{\conf{C}}{\conf{D}}}
                               & \equiv & \tm{\ppar{\conf{D}}{\conf{C}}}
    \\
    \LabTirName{SC-ParAssoc}   & \tm{\ppar{\conf{C}}{(\ppar{\conf{D}}{\conf{E}})}}
                               & \equiv & \tm{\ppar{(\ppar{\conf{C}}{\conf{D}})}{\conf{E}}}
  \end{array}
\end{mathpar}

\subsubsection{Configuration reduction}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{E-New}   & \tm{\plug{\conf{F}}{\new\;\unit}}
                         & \cred & \tm{\res{x}{y}{(\plug{\conf{F}}{\pair{x}{y}})}}
    \\
    \LabTirName{E-Spawn} & \tm{\plug{\conf{F}}{\spawn\;V}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\child\;V\;\unit}}
    \\
    \LabTirName{E-Send}  & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\send\;{\pair{V}{x}}}}
                           {\plug{\conf{F'}}{\recv\;{y}}})}}
                         & \cred & \tm{\res{x}{y}{(\ppar
                                   {\plug{\conf{F}}{x}}
                                   {\plug{\conf{F'}}{\pair{V}{y}}})}}
    \\
    \LabTirName{E-Close} & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\wait\;{x}}}
                           {\plug{\conf{F'}}{\close\;{y}}})}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\plug{\conf{F'}}{\unit}}}
  \end{array}
  \\
  \inferrule*[lab=E-LiftC]{
    \tm{\conf{C}}\cred\tm{\conf{C'}}
  }{\tm{\plug{\conf{G}}{\conf{C}}}\cred\tm{\plug{\conf{G}}{\conf{C'}}}}

@@

\begin{restatablelemma}{lempgvopenprogressterms}[Open Progress, $\tred$]
  \label{lem:pgv-open-progress-terms}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    $\tm{M}$ is a value;
  \item[Step]
    There exists some $\tm{N}$ such that $\tm{M}\tred\tm{N}$; or
  \item[Blocked]
    There exists some $\tm{E}$ and $\tm{R}$ such that $\tm{M}=\tm{\plug{E}{R}}$.
  \end{description}
\end{restatablelemma}
\begin{proof}
  \todo{Write proof.}
\end{proof}

\begin{restatabletheorem}{thmpgvopenprogressconfs}[Open Progress, $\cred$]
  \label{thm:pgv-open-progress-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\phi\;V}$;
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$; or
  \item[Blocked]
    There exist $\tm{x_i}$ and $\tm{y_i}$ for $0\leq{i}\leq{n}$, and $\tm{\phi_j}$ and $\tm{R_j}$ for $0\leq{j}\leq{m}$, such that $\tm{\conf{C}}=\tm{\res{x_1y_1\dots x_ny_n}{}{(\phi_1R_1 \parallel\dots\parallel \phi_mR_m)}}$ and for each $\tm{R_j}$ there exists some $\tm{a_j}\in\fn(\ty{\Gamma})$ such that $\blocked(\tm{a_j},\tm{R_j})$.
  \end{description}
\end{restatabletheorem}
\begin{proof}
  \todo{Write proof.}
\end{proof}

>>>>

\subsubsection{Syntactic Sugar}%
\label{sec:pgv-syntax-sugar}
We define the type of pure functions, \ie functions which perform no communication, and types for internal and external choice. Furthermore, we define term constructs for sequential composition, let-binding, various pattern matching lambda abstractions, fork, which combines channel creation and thread spawning in one construct, and internal and external choice.
\[
\begin{array}{lcl}
  \ty{\tylolli{T}{U}}
  & \elabarrow & \ty{\tylolli[\cs{\ptop},\cs{\pbot}]{T}{U}} \\
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}} \\
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
  \\
  \tm{\andthen{M}{N}}
  & \elabarrow & \tm{\letunit{M}{N}} \\
  \tm{\letbind{x}{M}{N}}
  & \elabarrow & \tm{(\lambda x.N)\;M} \\
  \tm{\lambda\unit.M}
  & \elabarrow & \tm{\lambda z.\letunit{z}{M}} \\
  \tm{\lambda\pair{x}{y}.M}
  & \elabarrow & \tm{\lambda z.\letpair{x}{y}{z}{M}} \\
  \tm{\fork}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\spawn\;{(\lambda\unit.x\;y)}}{z}}} \\
  \tm{\select{\ell}}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\close\;(\send\;{\pair{\ell\;y}{x}})}{z}}} \\
  \multicolumn{3}{l}{\tm{\offer{L}{x}{M}{y}{N}}\elabarrow} \\
  \multicolumn{3}{l}{
  \qquad\tm{\letpair{z}{w}{\recv\;{L}}{\andthen{\wait\;{w}}{\casesum{z}{x}{M}{y}{N}}}}} \\
  \tm{\offeremp{L}}
  & \elabarrow & \tm{\letpair{z}{w}{\recv\;L}{\andthen{\wait\;{w}}{\absurd{z}}}}
\end{array}
\]

@@

\subsubsection{Structural congruence}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{SC-LinkSwap}   & \tm{\plug{\conf{F}}{\link\;{\pair{x}{y}}}}
                               & \equiv & \tm{\plug{\conf{F}}{\link\;{\pair{y}{x}}}}
    \\
    \LabTirName{SC-ResLink}    & \tm{\res{x}{y}{(\phi\;\link\;\pair{x}{y})}}
                               & \equiv & \tm{\phi\;\unit}
    \\
    \LabTirName{SC-ResSwap}    & \tm{\res{x}{y}{\conf{C}}}
                               & \equiv & \tm{\res{y}{x}{\conf{C}}}
    \\
    \LabTirName{SC-ResComm}    & \tm{\res{x}{y}{\res{z}{w}{\conf{C}}}}
                               & \equiv & \tm{\res{z}{w}{\res{x}{y}{\conf{C}}}}
    \\
    \LabTirName{SC-ResExt}     & \tm{\res{x}{y}{(\ppar{\conf{C}}{\conf{D}}})}
                               & \equiv & \tm{\ppar{\conf{C}}{\res{x}{y}{\conf{D}}}},
                                          \text{ if }{\tm{x},\tm{y}\notin\fv(\tm{\conf{C}})}
    \\
    \LabTirName{SC-ParNil}     & \tm{\ppar{\conf{C}}{\child{\unit}}}
                               & \equiv & \tm{\conf{C}}
    \\
    \LabTirName{SC-ParComm}    & \tm{\ppar{\conf{C}}{\conf{D}}}
                               & \equiv & \tm{\ppar{\conf{D}}{\conf{C}}}
    \\
    \LabTirName{SC-ParAssoc}   & \tm{\ppar{\conf{C}}{(\ppar{\conf{D}}{\conf{E}})}}
                               & \equiv & \tm{\ppar{(\ppar{\conf{C}}{\conf{D}})}{\conf{E}}}
  \end{array}
\end{mathpar}

\subsubsection{Configuration reduction}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{E-Link}  & \tm{\res{x}{y}{(\ppar{\plug{\conf{F}}{\link\;\pair{w}{x}}}{\conf{C}})}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\subst{\conf{C}}{w}{y}}}
    \\
    \LabTirName{E-New}   & \tm{\plug{\conf{F}}{\new\;\unit}}
                         & \cred & \tm{\res{x}{y}{(\plug{\conf{F}}{\pair{x}{y}})}}
    \\
    \LabTirName{E-Spawn} & \tm{\plug{\conf{F}}{\spawn\;V}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\child\;V\;\unit}}
    \\
    \LabTirName{E-Send}  & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\send\;{\pair{V}{x}}}}
                           {\plug{\conf{F'}}{\recv\;{y}}})}}
                         & \cred & \tm{\res{x}{y}{(\ppar
                                   {\plug{\conf{F}}{x}}
                                   {\plug{\conf{F'}}{\pair{V}{y}}})}}
    \\
    \LabTirName{E-Close} & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\wait\;{x}}}
                           {\plug{\conf{F'}}{\close\;{y}}})}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\plug{\conf{F'}}{\unit}}}
  \end{array}
  \\
  \inferrule*[lab=E-LiftC]{
    \tm{\conf{C}}\cred\tm{\conf{C'}}
  }{\tm{\plug{\conf{G}}{\conf{C}}}\cred\tm{\plug{\conf{G}}{\conf{C'}}}}

@@

\begin{restatablelemma}{lempgvopenprogressterms}[Open Progress, $\tred$]
  \label{lem:pgv-open-progress-terms}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    $\tm{M}$ is a value;
  \item[Step]
    There exists some $\tm{N}$ such that $\tm{M}\tred\tm{N}$; or
  \item[Blocked]
    There exists some $\tm{E}$ and $\tm{R}$ such that $\tm{M}=\tm{\plug{E}{R}}$.
  \end{description}
\end{restatablelemma}
\begin{proof}
  \admit
\end{proof}

\begin{restatabletheorem}{thmpgvopenprogressconfs}[Open Progress, $\cred$]
  \label{thm:pgv-open-progress-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\phi\;V}$;
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$; or
  \item[Blocked]
    We have $\tm{\conf{C}}\equiv\tm{\res{x_1y_1\dots x_ny_n}{}{(\phi_1R_1 \parallel\dots\parallel \phi_mR_m)}}$,\\
    and for some $\tm{R_j}$ and $\tm{a_j}\in\fn(\ty{\Gamma})$, $\blocked(\tm{a_j},\tm{R_j})$.
  \end{description}
\end{restatabletheorem}
\begin{proof}
  \admit
\end{proof}
